\section{Application scenario outlook}
During the design of the NAX token model we focused on a fair and effective issuance model which respects fairness, legitimacy and authority of the asset. Combined with the ecological characteristics of Nebulas, we chose distribute more incentives to application scenarios. For example, motivation and utilization scenarios in application scenarios can be varied, diverse, and unique.

In this chapter, we will look at some prospects for existing or upcoming scennarios within Nebulas. Through the outlook of the main application scenarios, we can clearly demostrate the tandem role of NAX in the Nebulas ecosystem.

\subsection{Ecological contribution incentive}
In the white paper, the contribution-proof consensus algorithm Proof of Devotion (PoD), the vision of Nebulas was shared: Fair value for all via decentralized collaboration, to the launch of the Go Nebulas platform in early 2019, Nebulas has been constantly explored ecosystem contribution. These have all been important steps forward for Nebulas to move further towards the creation of the Autonomous Metanet. To this end, we put forward a unique pledge investment fund as a proof of equity incentive which can be applied to different scenarios.
The specific operation is to pledg the fund by the project investment fund (usually in the form of NAS). The NAX equity of this part of the fund pledge will be used as the NAX incentive equity fund for ecosystem scenario.

\subsubsection{Go Nebulas Incentive}
The Nebula Foundation will invest no less than $3 million in NAS to fund projects on the Go Nebulas platform, and will be ready to invest additional funds on demand. This amount of money can be invested in pledging and the resulting equity will be used to incentivize large and small contributions of users that are made on the Go Nebulas platform, i.e. in addition to receiving NAS funds as a reward, they will also receive NAX incentives under the rules established by the Go Nebulas platform as an equity right to contribute to the Nebula ecosystem. The corresponding rights and governance can be exercised in the Nebulas ecosystem. Detailed incentives will be developed by Go Nebulas' operations team managers or community participants.
Incentives can be divided into the following categories:

\begin{enumerate}[\hspace{1cm}(a)]
  \item core infrastructure
  \item market expansion
  \item promotion
  \item creating proposals and participation
\end{enumerate}

In addition to being an important means of investing within community building and reciving NAX incentives, the Go Nebulas platform is an important use scenario for NAX. Utility scenarios include (but not limited to) the following categories:
\begin{enumerate}[\hspace{1cm}(a)]
  \item Create and initiating a proposal
  \item passing and rejecting proposals
  \item pledge twords the progress of the project
\end{enumerate}

\subsubsection{Foundation Core Member Incentive}
Members of the Nebulas Foundation's core team, including part-time staff, will receive NAX benefits from the Foundation's pledge as additional contribution in addition to receiving their appropriate salary.


\subsection{On-chain governance scenario}
Within the Nebulas ecosystem, there will be a variety of selection and election activities. For each event, we will encourage greater participation and during these events, different methods of voting will be used such as destroying or returning utilized NAT which will motivate users for their participation.

For example, how to handle the 35 million NAS community reserve fund will become an early activity utilizing NAT in which the community contributes solutions and the community decides which solution will be put into action. The Nebulas Foundation has proposed to destroy this fund and one possible solution is to launch a NAX utilized monthly vote to decide how much of the fund to be destroyed. For example, if (\alpha\) \% , \(\alpha\) \% is the current NAS pledge rate in the share of liquidity. Of course, the community can also provide a more effective program, and then jointly decide the processing of this part of the assets.

\subsection{Node campaign}
With the advancement of the Nebulas in the development of PoD, the decentralization of Nebulas is a current and inevitable path. NAX will likely become a mechanism and credential for the Nebulas node campaign. It can effectively combine the main network PoD technology innovation into the foundation and direction of the new consensus algorithm. The possible ways for a node to proceed are as follows:
\begin{enumerate}[\hspace{1cm}(a)]
  \item node candidates are selected via NAX vote
  \item participants in the node campaign will need to destroy a corresponding amount of NAX and pledge NAS
  \item the community can crowdfend NAX to become a node and receive the benefits of block rewards
\end{enumerate}

\subsection{Ecosystem promotion}
Developed by the Nebulas Foundation, the basic ecosystem products are an important  element for the ecological use of the Nebulas blockchain. These products include the current and future Nebulas products incubated by the Foundation, such as: NAS nano Pro, NASnano, web explorer, Nebulas DEX, etc... As Next DAO advances and community governance progresses, there will be more and more NRC20 Tokens and governance attempts within the community. These currencies have strong a demand for ecological tools such as NAS nano Pro and Explorer. With limited resources and in order to make Nebulas ecosystem related products developed more improved projects, it is possible to use NAX as a platform to select excellent projects tools and funding. These funds can also be used for activities and incentives for ecological projects. Funding is used to invest in the construction of the platform.
